---
title: "Data Science for Public Policy"
subtitle: "Assignment04"
author: "Lingxi Li - ll1188,
         Talia Stringfellow -tjs296"
execute:
  warning: false
format:
  html:
    embed-resources: true
---

## Research question

The Paris Agreement was adopted at the 21st United Nations Climate Change Conference (COP21) on December 12, 2015. Since then, the world has accelerated its path for energy transition. Our interest lies in the specific and important component of world energy, electricity. We want to examine how different countries generate electricity before and after 3 years of the adoption of The Paris Agreement.

## Data resource

We refer to the energy data set from Our World In Data to analyze the question. The resource link is: <https://ourworldindata.org/explorers/energy>

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
