---
title: "Data Science for Public Policy"
subtitle: "Assignment04"
author: "Lingxi Li - ll1188,
         Talia Stringfellow -tjs296"
execute:
  warning: false
format:
  html:
    embed-resources: true
---

## Research question

The BRICS nations group was create to "bring together the world's most important 
developing countries, to challenge the political and economic power of the wealthier 
nations of North America and Western Europe" and originally consisted of Brazil, 
Russia, India, and China (BBC, 2024). In 2010, South Africa joined as a member 
(effectively turning "BRIC" into how we know it today, "BRICS"). For our research,
we examined data from the Energy Data Explorer via Our World Data to observe
energy use, per person, within the five nations between the years of 2010 and 2018. 
Notably, in 2015 all these nations signed onto the Paris Climate Accord, an
international treaty dedicated to addressing the climate crisis. 

It is interesting to observe the energy usage of these BRICS nations as they are
leading developing countries. Often, when studying climate change and problem solving
for solutions, we hear contention between developed and developing countries on the 
matters of carbon emissions and pollution. Indeed, developed countries contributed 
disproportionately to the current climate crisis today (countries that lead the 
Industrial Revolution - a well establised tipping point for the climate crisis), 
and developing contries lament the stringent impositions of these types of Accords 
for the costs it potentially has on their own ability to grow and develop. 

According to United Nations, "most electricity is still generated by burning fossil 
fuels, but cleaner sources of energy are gaining ground. About 29 percent of electricity currently comes from renewable sources, such as wind and solar, which nature will replenish and which emit little to no greenhouse gases or pollutants into the air. The cost of renewable-energy technologies also keeps falling, making renewables the most affordable source of power today." Thus, we found decided to investigate how electricity usage has changed over the 8 
year period. And see how the developing countries have transformed (or not) in their
electricity usage. 

## Data resource

We refer to the energy data set from Our World In Data to analyze the question. The resource link is: <https://ourworldindata.org/explorers/energy>

Step1：Clean the data
```{r}
library(tidyverse)
data<-read_csv("data/energy_data.csv")
data<-data %>% 
  filter(country=="China"|country=="Brazil"|country=="Russia"|country=="India"|country=="South Africa",
    year>=2010 & year<=2018,
    !is.na(population),
    !is.na(gdp))
```

Graph 1:
BRICS's total electricity generation as share of primary energy between 2010 and 2018

```{r}
library(ggplot2)
data %>% 
  ggplot(aes(x = year, y= electricity_share_energy))+
  geom_line(aes(color=(country)),alpha=0.8,size=0.7)+
  scale_y_continuous(limit=c(10,23))+
  theme_minimal()+
  theme(plot.caption = element_text(size = 6)) +
  labs(x = "Year", y = "Electricity as Percent Share of Primary Energy \n(percentage point)", 
       title = "Total Electricity Generation for BRICS Countries",
       subtitle = "As Percentage Share of Total Primary Energy Consumption from 2010 to 2018",
       caption="'Energy use per person' - U.S. Energy Information Administration (2023) \n Energy Institute - Statistical Review of World Energy (2023) \n Population based on various sources (2023) via Our World Data \n OurWorldInData.org/energy") +
  scale_color_discrete(name = "Country")
```
This is a graphic of the total electricity generation as percentage share of 
direct primary energy consumption across BRICS nations from the year 2010 to 2018. 
In 2015, these countries signed the Paris Climate Accord and since you can see a 
steeper increase in Brazil, China, India. South Africa and Russia's share of 
electricity has remained consistent, though has dropped below 2010 shares in 2018. 
This data is interesting to contextualize the question of electricity energy as 
a share of each country's energy usage, but we will dive deeper in the subsequent 
graphs. 

Graph 2:
BRICS electricity demand from 2010 to 2018

```{r}
data %>% 
ggplot(aes(x=country,y=electricity_demand))+
  geom_boxplot(aes(color=country),alpha=0.5)+
  theme_minimal()+
  theme(plot.caption = element_text(size = 6))+
  labs(x = "Country", y = "Electricity Demand \n (measured in terawatt-hours)", 
       title = "Electricy Demand for BRICS from 2010 to 2018",
       caption="'Energy use per person' - U.S. Energy Information Administration (2023) \n Energy Institute - Statistical Review of World Energy (2023) \n Population based on various sources (2023) via Our World Data \n OurWorldInData.org/energy")
```
This graph represents BRICS country absolute amount of electricity demand range 
between 2010 and 2018. China stands out with the largest electricity demand, with 
with the largest variance over the 18 year period. Brazil, Russia and South Africa
have almost no variance over the years and hover below 1000 terrewatts per hour.
Variance is noticable in India. Given that the two countries with highest variance 
are also the most populated, we hypothesize that population size affects Electricy
Demand variance. 

Graph 3:
BRICS's carbon intensity change between 2010 and 2018

```{r}
data %>% 
ggplot(aes(x = country, y = carbon_intensity_elec,fill = factor(year))) +
  geom_bar(stat = "identity", position = "dodge", alpha=0.9)+
  scale_fill_brewer(palette = "BlGn")+
  theme_grey()+
  theme(plot.caption = element_text(size = 6))+
  labs(x = "Country", 
       y = "Carbon Intensity of Electricity Generation", fill = "Year",
       title="Carbon Intensity of Electricity for BRICS from 2010 to 2018",
       subtitle="(Carbon intensity of Electricity Generation \n measuered in grams of CO2 equivalents per kilowatt-hour)",
       caption="'Energy use per person' - U.S. Energy Information Administration (2023) \n Energy Institute - Statistical Review of World Energy (2023) \n Population based on various sources (2023) via Our World Data \n OurWorldInData.org/energy") 

```
The Carbon Intensity of Electricity Generation is measured in grams of CO₂ equivalents per kilowatt-hour by country between the years of 2010 to 2018. The ten year range 
allows us to observe longterm change. Brazil reaches a peak in 2014 and we observe
a steady decline starting in 2015. In China, the peak is in 2011 followed by a steady decrease. 
This pattern is also observable in South Africa - the country with the largest 
carbon intensity, though with a less linear decline. Russia remains stagnant at
just below 400 grams of C0₂ equivalents per kilowatt-hour. Finally, India has a 
somewhat consistant, though rising, overall trend in CO₂ equivalents per kilowatt-hour.
Post-2015, we expected that the intensity of cabon for electricity generation would 
decrease as they invest in renewable resources for generating electricty but the 
observable change is minimal. 

Graph 4:
How BRICS's carbon intensity change with its electricity import from 2010 to 2018
```{r}
data %>% 
  group_by(country) %>% 
  ggplot(aes(x = year, y= net_elec_imports)) +
  geom_point(aes(size=carbon_intensity_elec,color=year),alpha=0.8) +
  geom_smooth(method="lm", se=F, size=0.5, color="black")+
  facet_wrap(~country)+
  labs(x = "Year", y = "Net Electrical Imports", 
       title = "Relationship between Carbon Intensity of Electricity Generation \n and Net Electrical Imports \n From 2010 to 2018",
       subtitle = "(Carbon Intensity measured in grams of CO2 equivalents per kilowatt-hour)",
       color = "Year", caption="'Energy use per person' - U.S. Energy Information Administration (2023) \n Energy Institute - Statistical Review of World Energy (2023) \n Population based on various sources (2023) via Our World Data \n OurWorldInData.org/energy") +
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.5), 
        plot.margin = margin(t = 20, r = 20, b = 20, l = 20), 
        plot.caption = element_text(size = 6))+
  scale_size_continuous(name = "C02 Intensity \n of Elec Gen",range=c(1,12))
```

Here we observe the relationship of net electricity imports on carbon intensity of 
electricity generation. As we expected, countries that import more than they 
export in electricity have lower carbon intensity of electricity generation - as
the generated carbon is occurring outside the nation. Brazil fluctuates below the 
250 grams of CO₂ equivalents per kilowatt-hour carbon intensity of electricity 
generation. India has transitioned from net possitive in imports of electricity 
has instead become an exporter falling below the zero threshold. All the while, their
CO2 intensity of electrical generaton has remained constant in the 400 grams of 
CO₂ equivalents per kilowatt-hour.


Sources Cited:
Brics: What is the group and which countries have joined? (2024, February 1). BBC. https://www.bbc.com/news/world-66525474

Nations, U. (n.d.). Generating power. United Nations; United Nations. https://www.un.org/en/climatechange/climate-solutions/cities-pollution


Data Source:
'Energy use per person' - U.S. Energy Information Administration (2023) Energy 
Institute - Statistical Review of World Energy (2023) Population based on various 
sources (2023) via Our World Data OurWorldInData.org/energy
